A community-maintained standard library of population genetic models

### 2020-04-21 response-to-reviewers.md

"Accurately" is subjective -- we're sure the reviewer can imagine much worse inferences! --
but in any case we've rephrased this bit to say
"While there is variation in accuracy among methods, populations, and individual replicates,
the methods generally infer back a good estimate
of the true effective population sizes of the simulations --
inferred values are mostly within a factor of two of the truth,
and many of the methods infer a bottleneck at the correct time."

> -Page 8, paragraph "Stdpopsim allows...": reword this first sentence

@@

We changed the sentence as follows:
"Using stdpopsim, we can readily compare performance on this benchmark to
that based on a different model of human history. "

> -Figure 3 caption: wrong citation, should be Sheehan and Song

The citation was for the genetic map, but we've added the citation to Sheehan and Song for the model (also in the caption of Figure 2).

> -Page 10, last sentence before "Multi-population demographic models" section: clarify what "this setting" is (both species I assume)

@@

We made the following change:  
"Accuracy is mixed among methods when doing inference on simulated data from these D. melanogaster
and A. thaliana models, and generally worse than what we
observe for simulations of the human genome."

> -Figure 4 captain: "or smc++" -> "and smc++" (some other figure captions have this too), I would also say "$x$-axis"

We made the suggested changes.

> -Page 12, first paragraph: include a reference where people could learn more about the effective population size vs. census size, random-mating models, etc

@@

We thank the reviewer for this suggestion.
However, we have realized that our use of "census size" here to describe the "true" simulated population size was a bit misleading,
as our intention was not to characterize these as actual "census" (as opposed to "effective") population sizes.
To avoid this confusion, we have changed the manuscript to now describe them as the "simulated population size". For example, this section now reads:

"However, because model misspecification
here is less severe  compared to the single-population case, we compare
our inferred population sizes only to the simulated population sizes (black line in
Figure 4C) and not the inverse coalescence rates."

We have, however, added more discussion of this point (with a citation to a review)
to the start of the Appendix.

> -Page 12 (and elsewhere): "By contrast" -> "In contrast"(?) I think both are technically correct though

We changed all instances of "by contrast" to "in contrast".

> -Page 12: sentence beginning with "Figure S4 shows..." is long, perhaps breakup or rephrase ("bottleneck into a European population" sounds odd to me.)

We changed this section to the following:  
"Figure S4 shows inference results using data simulated under
the OutOfAfrica_2L06 model. This model includes an ancestral population in
Africa from which a European population splits off following a bottleneck, with no
post-divergence gene flow between the African and European population (Figure S4A)."

> -Page 12: "Europe population" -> "European population"

> -Page 12: S7, S4, S6 are mentioned in a different order than they appear in the supplement (I understand why but maybe revisit this part)

@@

> -Page 12: S7, S4, S6 are mentioned in a different order than they appear in the supplement (I understand why but maybe revisit this part)

We reordered the figures to make sure they were referenced in the same order they appear in the supplement.

> -Page 13: "overfit the YRI history" do you mean overfit in a technical sense?

Really, we just mean that the inferred history has more population size changes
than the truth did;
we've change this to "overcomplicate the simple YRI history".

> -Page 14: "Method quality control" section. Could you say a bit more about how Developer B would be identified? Someone in the consortium or someone else in the community? What kind of leadership structures are in place? (Maybe the goal is to make this a bit more distributed?) And just to be clear, Developer B would not have access to Developer A's implementation of the model while they were independently implementing it, right?

We've clarified this to say that "Developer B (perhaps found by requesting review from the broader Consortium)".
The process is not blinded in any way -- developer B *could* look at developer A's implementation --
but we don't think this will be a problem in practice.

> -Page 16, line 6: "population 1 after"?

@@

>
> -Page 16: S5 -> Figure S5

We corrected this mistake.

>
> -Page 17: "with making" -> "for making"?

Thanks! We corrected this.

> -Figure S2 caption: move "and" to before MSMC (in a few other figure captions too)

@@

We made the suggested change.

> -Figure S6: explain x-axis "MIG_AF_EU" and "MIG_EU_AF". I assume these are directional migration rates

We added a sentence to the caption better explaining this figure.

> -Figure S9: unreadable when printed (not sure it adds a lot)
